Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2020-10-08 minimax.tex

\section{Related Work}
\label{sec:related}
%The work of \citet{Cailloux2014} provides elicitation methods for a quite general class of rules based on weak orders.
%it is possible to derive dominance relations (akin to stochastic dominance) that allow to eliminate some alternatives since they will be less preferred than another one for any instantiation of the weights \citep{Stein1994}.
%Among others, Llamazares and Pe{\~{n}}a have considered  the problem of dealing with underspecified weights in positional scoring rules.

@@

\subsection{Absolute evaluation of Pessimistic strategy}
\label{sec:lowRegret}
\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-number-alignment = center]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]}
			\toprule
			{m} & {n} & {$\frac{n}{10}$} & {$k_{\MMR}$} & {$0.4 m^{1.6} n$} \\
			\midrule
			5 & 10 & 1.0 & 60 &  55 \\
			5 & 15 & 1.5 & 80 &  83 \\
			5 & 20 & 2.0 & 110 &  110 \\
			10 & 20 & 2.0 & 340 &  341 \\
			10 & 30 & 3.0 & 527 &  512 \\
			15 & 30 & 3.0 &  &  991 \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Number of questions needed by Pessimistic strategy to reach $\MMR=\frac{n}{10}$ (represented by $k_{\MMR}$), for various problem sizes.}
	\label{tab:lowRegret}
\end{table}

@@

\subsection{Value of information comparison}
\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
			\toprule
			{p} & {Com. Fst.} & {sd} & {Vot. Fst.} & {sd} \\
			\midrule
			0 & 0.66 & 0.67 & 0.65 & 0.65  \\
			50 & 1.23 & 1.46 & 0.8 & 0.79 \\
			100 & 2.03 & 1.56 &  &  \\
			150 & 3.41 & 1.79 & 4.07 & 1.51 \\
			200 &   &  &  &  \\
			250 & 8.4 & 1.86 & 	& \\
			300 &&&& \\
			350 &&&& \\
			400 &&&& \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Average $\MMR$ in problems of size $(10, 20)$ after $400$ questions and $10$ runs. Where $p$ represents the number of questions asked to the chair.}
	\label{tab:twoP400}
\end{table}

>>>>

\section{Related Work}
\label{sec:related}
The recent growing interest in voting theory has also led to an increase in attention to its problems. One of these, the full information assumption; which has driven an increasing number of authors to question its validity. \citet{Conitzer2005} have studied the complexity of communication, using different voting rules, determining lower and upper bounds for it. They showed that, in the worst case, the agents should send their complete set of preference for most of the rule investigated. Considering then, cases where the information of agent preferences is only partial, \citet{Konczak05} have proposed a way to compute possible and necessary winners. They also showed that, even though this computation is hard in the general case, their method is polynomial in case of positional scoring rule. Later on, for the necessary winner problem, other authors have proposed polynomial-time algorithms when using maximin and Bucklin \citep{Xia2008}; sufficient conditions that assure tractability have been proved \citep{Pini2007}; and the uncertainty in weights has been considered \citep{Walsh2007,Viappiani2018}.
From this starting point several studies on elicitation of agent preferences have been proposed \citep{Naamani-Dery2015,Kalech2011,Lu2011,Pini2009,Benabbou2016,Cailloux2014,Dey2016,Dey2016_2}, and analysis on when to stop the elicitation process have been conducted \citep{Walsh2009,Conitzer2009}. Although more interest

Although more interest has been shown in the incompleteness of agent preferences, several authors have considered scenarios where the voting rule is partially defined.  \citep{Stein1994, Viappiani2018}. Among others, \citet{Llamazares2013} have considered  the problem of dealing with variable weights in positional scoring rules.

In this context, questions on the manipulability of voting rules have begun to arise. In fact, studies on the reactions of agents after others actions have been proposed \citep{Endriss2016,Dey2018,Dey2018_2}. It is worth precising that, in our work, we consider the agents to give their preferences in a secret way.

@@

\subsection{Absolute evaluation of Pessimistic strategy}
\label{sec:lowRegret}
\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-number-alignment = center]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]}
			\toprule
			{m} & {n} & {$\frac{n}{10}$} & {$k_{\MMR}$} & {$0.4 m^{1.6} n$} \\
			\midrule
			5 & 10 & 1.0 & 60 &  55 \\
			5 & 15 & 1.5 & 80 &  83 \\
			5 & 20 & 2.0 & 110 &  110 \\
			10 & 20 & 2.0 & 340 &  341 \\
			10 & 30 & 3.0 & 527 &  512 \\
			15 & 30 & 3.0 & 919 &  991 \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Number of questions needed by Pessimistic strategy to reach $\MMR=\frac{n}{10}$ (represented by $k_{\MMR}$), for various problem sizes.}
	\label{tab:lowRegret}
\end{table}

@@

\subsection{Value of information comparison}
\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
			\toprule
			{p} & {Com. Fst.} & {sd} & {Vot. Fst.} & {sd} \\
			\midrule
			0 & 0.66 & 0.67 & 0.65 & 0.65  \\
			50 & 1.23 & 1.46 & 0.8 & 0.79 \\
			100 & 2.03 & 1.56 & 1.88 & 1.02  \\
			150 & 3.41 & 1.79 & 4.07 & 1.51 \\
			200 & 4.61	& 1.35  & 6.53 & 2.0  \\
			250 & 8.4 & 1.86 & 	7.69 & 1.24 \\
			300 &11.07 & 0.86& 11.87 & 1.25 \\
			350 &&&15.59 & 0.6 \\
			400 &20.0 & 0.0 & 20.0 & 20.0 \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Average $\MMR$ in problems of size $(10, 20)$ after $400$ questions and $10$ runs. Where $p$ represents the number of questions asked to the chair.}
	\label{tab:twoP400}
\end{table}
